---
title: "Offense"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---



```{r, include=FALSE}
# Installing Libraries 
#install.packages(c("tidyr", "dplyr", "knitr", "tidyverse", "yaml"))
library("tidyr")
library("yaml")
library("dplyr")
library("knitr")
library("tidyverse")
library("tinytex")
library("ggplot2")
```

```{r, include=FALSE}
# Reading Data
mudcatsRaw <- read.csv("https://raw.githubusercontent.com/bmswnson/Mudcats/main/Data/currentStats.csv")
```


```{r, include=FALSE}
# Adding Full Names
mudcatsRaw$fullName <- paste(mudcatsRaw$First, mudcatsRaw$Last, sep = " ")
```



```{r, include=FALSE}
# Subsetting Stats
offense <- mudcatsRaw %>% 
  select(Last, GP, PA, AB, H, X1B, X2B, X3B, HR, RBI,
         R, HBP, AVG, ROE, FC, OBP, SLG, OPS, PA.BB, 
         BB.K, C., K.L, SB, CS, SB.)
offenseSelect <- mudcatsRaw %>%
  select(fullName, Last, AVG, GP, PA, AB, H, X1B, X2B, X3B, HR, RBI,
         R, SB, HBP,  SLG, OPS, OBP, QAB.) %>% 
  rename("singles" = X1B, 
         "doubles" = X2B, 
         "triples" = X3B) 
#removing percentage off of qab percentage 
offenseSelect$QAB. <- str_sub(offenseSelect$QAB., 1, nchar(offenseSelect$QAB)-1)
offenseSelect$QAB. <- as.numeric(offenseSelect$QAB.)
```



# Team

## Tables

### At Bats
```{r}
abTable <- offenseSelect %>%
  select(Last, AB) %>%
  filter(Last != "Totals")
as.data.frame(abTable[order(abTable$AB, decreasing = TRUE),])
```


### Quality At Bats
```{r}
qabTable <- offenseSelect %>%
  select(Last, QAB.) 
as.data.frame(qabTable[order(qabTable$QAB., decreasing = TRUE),])

```

### Average
```{r}
avgTable <- offenseSelect %>%
  select(Last, AVG) 
as.data.frame(avgTable[order(avgTable$AVG, decreasing = TRUE),])

```

### OBP
```{r}
obpTable <- offenseSelect %>%
  select(Last, OBP) 
as.data.frame(obpTable[order(obpTable$OBP, decreasing = TRUE),])

```

## Graphs


### At Bats
```{r}
abGraph <- offenseSelect %>%
  filter(Last != "Totals")
ggplot(data = abGraph, aes(x = fullName, y = AB, label = Last)) + 
  geom_text(size = 2.5, vjust = 2) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, size = 0)) + 
  ggtitle(paste("At Bats"))
  
```


### Average
```{r}
ggplot(data = offenseSelect, aes(x = fullName, y = AVG, label = Last)) + 
  geom_text(size = 2.5, vjust = 2) +
  geom_point() + 
  scale_y_continuous(breaks = seq(0,1,.05)) +
  ylim(0, .75) +
  scale_x_discrete(expand = c(.04, .08)) +
  theme(axis.text.x = element_text(angle = 90, size = 0)) + 
  ggtitle(paste("Team Averages"))
  
```

### Quality At Bats Percentage
```{r}
ggplot(data = offenseSelect, aes(x = fullName, y = QAB., label = Last)) + 
  geom_text(size = 2.5, vjust = 2)  +
  geom_point()  +
  theme(axis.text.x = element_text(angle = 90, size = 0)) + 
  ggtitle(paste("Quality At Bats Percentage")) 
  
```

## Team Leaders (Inlcludes those in 80th percentile or above)

### Average
```{r}
avgLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(AVG, .8) < AVG) %>%
  select(fullName, AVG) 
as.data.frame(avgLead[order(avgLead$AVG, decreasing = TRUE),])
```

### At Bats
```{r}
absLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(AB, .8) < AB) %>%
  select(fullName, AB) 
as.data.frame(absLead[order(absLead$AB, decreasing = TRUE),])
```

### Hits
```{r}
hLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(H, .8) < H) %>%
  select(fullName, H) 
as.data.frame(hLead[order(hLead$H, decreasing = TRUE),])
```


### Singles
```{r}
singlesLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(singles, .8) < singles) %>%
  select(fullName, singles) 
as.data.frame(singlesLead[order(singlesLead$singles, decreasing = TRUE),])
```

### Doubles
```{r}
doublesLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(doubles, .5) < doubles) %>%
  select(fullName, doubles) 
as.data.frame(doublesLead[order(doublesLead$doubles, decreasing = TRUE),])
```

### Triples
```{r}
triplesLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(triples, .5) < triples) %>%
  select(fullName, triples) 
as.data.frame(triplesLead[order(triplesLead$triples, decreasing = TRUE),])
```

### Homers
```{r}
hrLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(HR, .5) < HR) %>%
  select(fullName, HR) 
as.data.frame(hrLead[order(hrLead$HR, decreasing = TRUE),])
```

### Stolen Bases 
```{r}
sbLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
 filter(quantile(SB, .5) < SB) %>%
  select(fullName, SB) 
as.data.frame(sbLead[order(sbLead$SB, decreasing = TRUE),])
```

### OPS
```{r}
opsLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
  filter(quantile(OPS, .8) < OPS) %>%
  select(fullName, OPS) 
as.data.frame(opsLead[order(opsLead$OPS, decreasing = TRUE),])
```

### On Base Percentage
```{r}
obsLead <- offenseSelect %>% 
  filter(Last != "Totals") %>%
   filter(quantile(OBP, .8) < OBP) %>%
   select(fullName, OBP) 
as.data.frame(obsLead[order(obsLead$OBP, decreasing = TRUE),])
```


# Individual Stats
## Dorsey
```{r}
offenseSelect %>%
  filter(Last == "Dorsey") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Gunkel
```{r}
offenseSelect %>%
  filter(Last == "Gunkel") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Gravy
```{r}
offenseSelect %>%
  filter(Last == "Gravdahl ") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Tommy
```{r}
offenseSelect %>%
  filter(Last == "Horan ") %>%
  select(-Last, -fullName) %>%
  kable()
```


## Howe
```{r}
offenseSelect %>%
  filter(Last == "Howe") %>%
  select(-Last, -fullName) %>%
  kable()
```


## Huntington
```{r}
offenseSelect %>%
  filter(Last == "Huntington") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Huseby
```{r}
offenseSelect %>%
  filter(Last == "Huseby") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Liking
```{r}
offenseSelect %>%
  filter(Last == "Liking") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Naugs
```{r}
offenseSelect %>%
  filter(Last == "Naugle") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Pill
```{r}
offenseSelect %>%
  filter(Last == "Pilon") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Reed
```{r}
offenseSelect %>%
  filter(Last == "Reed") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Big Chungus
```{r}
offenseSelect %>%
  filter(Last == "Sayles") %>%
  select(-Last, -fullName) %>%
  kable()
```

## Schwinner
```{r}
offenseSelect %>%
  filter(Last == "Stratton") %>%
  select(-Last, -fullName) %>%
  kable()
```

## B Weids
```{r}
offenseSelect %>%
  filter(Last == "Weidieman") %>%
  select(-Last, -fullName) %>%
  kable()
```

